---
title: "Syllabus"
draft: false
date: '2020-11-16T13:00:00'
menu:
  crcj9130:
    parent: Syllabus
    weight: 2
linktitle: Course Schedule
toc: true
type: docs
weight: 2

output: md_document
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(cache=FALSE)
knitr::opts_chunk$set(fig.path='figs/')
knitr::opts_chunk$set(cache.path='_cache/')
knitr::opts_chunk$set(warning=F, message=F)
# knitr::opts_knit$get(kable.force.latex = TRUE)
```



```{r dates_bib, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='pdf')
mon <- as.Date("2021-01-11")

advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 ttue <- obj + 1 + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 ttue <- format(ttue, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%2d", adv)
 tmp <- paste("Week ",zadv,sep='',", ", ttue)
 return(tmp)
}

library(RefManageR)
# library(knitcitations)
# library(rcrossref)
bib <- ReadBib("master.bib")
myopts <- BibOptions(bib.style = "authoryear", sorting="ynt", style="latex", first.inits=TRUE, max.names = 20)

```

## Class Schedule

### `r advdate(mon, 1)`: Syllabus & Course Overview
```{r, echo = FALSE, results="asis"} 
bib[author = "schwartz", "meares2020"]
``` 

### `r advdate(mon, 2)`: Police Culture, Part I
```{r, echo = FALSE, results="asis"}
bib["sierra2019", "sierra2016"]
```  

|    \color{ForestGreen}*Guest Speaker: Dr. Michael Sierra-Arévalo, University of Texas*\color{black}

### `r advdate(mon, 3)`: Police Culture, Part II
```{r, echo = FALSE, results="asis"}
bib["cranklangworthy1992", "cheng2020"]
``` 

|    \color{ForestGreen}*Guest Speaker: Tony Cheng, Yale University*\color{black}

### `r advdate(mon, 4)`: The "Ferguson/Floyd Effect"
```{r, echo = FALSE, results="asis"} 
bib["shjarback2017", "skoy2020"]
``` 

|    \color{ForestGreen}*Guest Speaker: Dr. John Shjarback, Rowan University*\color{black}

### `r advdate(mon, 5)`: Racial Disparities
```{r, echo = FALSE, results="asis"} 
bib["gaston2019a", "gaston2019b"]
``` 

|    \color{ForestGreen}*Guest Speaker: Dr. Shytierra Gaston, Georgia State University*\color{black}

### `r advdate(mon, 6)`: Misconduct and Accountability
```{r, echo = FALSE, results="asis"} 
bib["chalfin2020", "white2013"]
``` 

|    \color{ForestGreen}*Guest Speaker: Dr. Aaron Chalfin, University of Pennsylvania*\color{black}

### `r advdate(mon, 7)`: Body-worn Cameras
```{r, echo = FALSE, results="asis"} 
bib["lum2020", "gaub2020"]
``` 

|    \color{ForestGreen}*Guest Speaker: Dr. Janne Gaub, University of North Carolina Charlotte*\color{black}

### `r advdate(mon, 8)`: Diversifying the Police
```{r, echo = FALSE, results="asis"} 
bib["ba2020", "riccucci2018"]
``` 

|    \color{ForestGreen}*Guest Speaker: Dr. Bocar Ba, University of California Irvine*\color{black}

### `r advdate(mon, 9)`: Procedural Justice and Legitimacy
```{r, echo = FALSE, results="asis"} 
bib["nagin2020", "nix2017"]
``` 

```{r, echo = FALSE, results="asis"} 
bib["wood2020"]
``` 

|    \color{ForestGreen}*Guest Speaker: Dr. Cody Telep, Arizona State University*\color{black}

### `r advdate(mon, 10)`
*Spring Break - No class*

### `r advdate(mon, 11)`: Evidence-based Policing
```{r, echo = FALSE, results="asis"} 
bib["haberman2019", "sherman2015"]
``` 

|    \color{ForestGreen}*Guest Speaker: Dr. Cory Haberman, University of Cincinnati*\color{black}

### `r advdate(mon, 12)`: Women in Policing
```{r, echo = FALSE, results="asis"} 
bib["todak2017", "schuck2014"]
``` 

|    \color{ForestGreen}*Guest Speaker: Dr. Natalie Todak, University of Alabama Birmingham*\color{black}

### `r advdate(mon, 13)`: Police in Schools
```{r, echo = FALSE, results="asis"} 
bib["gottfredson2020", "fisher2020"]
``` 

|    \color{ForestGreen}*Guest Speaker: Dr. Ben Fisher, University of Louisville*\color{black}

### `r advdate(mon, 14)`: The Network Dynamics of Policing
```{r, echo = FALSE, results="asis"} 
bib["ouellet2019", "zhao2020"]
``` 

|    \color{ForestGreen}*Guest Speaker: Dr. Marie Ouellet, Georgia State University*\color{black}

### `r advdate(mon, 15)`
***Student presentations***  
***Research proposals due***
